### 2016-05-14 sec1_introduction_bk.tex
Introduction Almost Done
Need resolve comments

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
\end{tabular} 
\caption{Existing co-movement patterns. The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the total number of objects, $|\mathbb{T}|$ is the total number of timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
clusters of objects in each snapshots are denoted using dotted circles.}
\label{fig:related_work}
\end{figure}

@@

We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
The temporal dimension is discretized into six snapshots. 
In each snapshot, the objects are clustered as shown in the dotted circle.
By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
the same constraints on the time duration. 
\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is a particular demand for a general platform to support all these co-movement patterns. The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performances degrade dramatically as the dataset size scales up. In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity. For instance, the
complexities of \emph{swarm} and \emph{platoon} are already exponential. 
Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

Therefore, our primary contributions in this paper are to close these two gaps. First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature. We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem. 
The \emph{loose connection} problem refers to the patterns that discovered 
are loosely-connected in the temporal domain. For example, in Figure~\ref{fig:platoon_weakpoint}, two objects $o_1, o_2$ 
would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
duration is $98$ timestamps apart, making the co-movement behavior very weak.
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$. By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?

%
\begin{figure}[h]
\center
\includegraphics[width=0.45\textwidth]{platoon_weakpoint.eps}
\caption{Loosely connected pattern in platoon and swarm. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
\label{fig:platoon_weakpoint}
\end{figure}

@@

Third, we conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

>>>>

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
clusters of objects in each snapshots are denoted using dotted circles. Each type of pattern has its parameters. 
$M$ denotes the minimum size of objects.
$K$ denotes the minimum size of timestamps.
$L$ denotes the minimum size of locally consecutive timestamps.}
\label{fig:related_work}
\end{figure}

@@

We compare and contrast these patterns using Figure~\ref{fig:related_work} as an example. 
In Figure~\ref{fig:related_work}, six trajectories are presented and 
the temporal domain is discretized into six snapshots. In each snapshots,
the objects are clustered as shown in the dotted circles. In this example, we
do not distinguish how the cluster is generated but focus on the 
differences on the pattern constraints. There are at most three parameters
required for each pattern, where $M$ is the minimum cardinality  of the object set;
$K$ is the minimum duration; $L$ is the minimum length for each locally consecutive
timestamps.

Both \emph{flock} and \emph{convoy} require two parameters $M$ and $K$. They
further enforce the duration of a pattern to be consecutive. As shown in the
Figure~\ref{fig:related_work}, $\{o_3,o_4:1,2,3\}$ are the only pattern that matches the requirement.
Differently, \emph{group} does not have the constraint for the minimum object size nor minimum duration. 
Indeed, \emph{group} aims to find the maximal set of objects whose duration is 
locally consecutive.
In Figure~\ref{fig:related_work}, three patterns are discovered to conform to $L$.  \emph{Platoon}
similarly uses $L$ as pattern parameter, but it further requires $M$ and $K$. In Figure~\ref{fig:related_work}, 
three patterns are discovered as \emph{platoon}s. It is notable that, due the differences in semantics,
\emph{platoon} discovers a different set of patterns from \emph{group}. For instance, a \emph{platoon} $\{o_3,o_4:1,2,3\}$
is not a \emph{group} since $\{o_3,o_4,o_5:2,3\}$ is already a \emph{group} making $\{o_3,o_4:1,2,3\}$ not maximal in object size.
On the other hand, although $\{o_3,o_4,o_5:2,3,\}$ is a \emph{group}, its
duration only consists of two timestamps, making it not a \emph{platoon}. \emph{Swarm} requires
$M$ and $K$ but it does not enforce any consecutiveness in the pattern duration. 
Due to such a relaxation, \emph{swarm} is able to find more results that
are not discovered by \emph{convoy} or \emph{platoon}. For instance, $\{o_2,o_3:3,4,6\}$ is a \emph{swarm}
with $M=2,K=3$. However, since its duration is not locally consecutive with size $2$, it is not a \emph{platoon}.
Similarly, since the duration is not even consecutive, it is not a \emph{convoy} neither.

%To better illustrate the temporal constraints of these 
%co-movement patterns, we design a scenario with six example trajectories in Figure~\ref{fig:related_work}.
%In the setting, the temporal dimension  is discretized into six snapshots. 
%In each snapshot, objects are clustered as shown in the dotted circles. We use $M$ to denote
%the minimum size of a object group, $K$ to denote the minimum number 
%of timestamps in a duration, $L$ to denote the minimum size of local-consecutive segments in a duration.
%
%\noindent\textbf{Global consecutiveness}: \emph{Flock} and \emph{convoy} patterns enforce the pattern duration to be \emph{global consecutive}. We discover one \emph{flock} and one \emph{convoy} pattern, which both correspond to $\{o_3,o_4:1,2,3\}$. It can be verified that no other object groups appears in more than three consecutive timestamps. 
%
%\noindent\textbf{Local consecutiveness}: \emph{Group} and \emph{platoon} patterns require the duration to be \emph{locally consecutive}. When setting $L = 2$,
%we observe three \emph{group} patterns and three \emph{platoon} patterns. Specifically, \emph{group} aims to find the
%pattern with maximal object set whose duration conforms to $L$ consecutiveness. Taking the pattern $\{o_3,o_4,o_5:2,3\}$ as an example. $\{o_3,o_4,o_5\}$ is indeed maximal. If another object, say $o_2$, is added to the group, the duration reduces to $\{3\}$ which is not $L$-consecutive. In fact, adding any other object to this group invalidates the $L$-consecutiveness. In contrary, \emph{platoon} finds the maximal object set whose duration is not only $L$-consecutive but also with size no less than $K$. Therefore, \emph{platoon} finds a different set of patterns. For example, $\{o_4,o_5:2,3,5,6\}$ is a \emph{platoon} pattern but not a \emph{group} pattern. This is because the object set $\{o_4,o_5\}$ is not maximal wrt. \emph{group}, as we can see that adding $o_3$ to the object set results in a larger \emph{group} pattern. Therefore, $\{o_4,o_5:2,3,5,6\}$ is not a \emph{group}.
%
%\noindent\textbf{No consecutiveness}: \emph{Swarm} pattern relaxes the consecutiveness in the duration. Thus as shown in the Figure, \emph{swarm} discover the most number of patterns. In particular, given the same $M$ and $K$, \emph{swarm} result covers all patterns discovered in \emph{flock}, \emph{convoy} and \emph{platoon}. Furthermore, it finds more patterns that are not covered by \emph{flock}, \emph{convoy} and \emph{platoon}. For instance, $\{o_5,o_6, 1,4,5\}$ is a \emph{swarm} but is neither a \emph{platoon} (with $L=2$) nor a \emph{convoy}.

%Therefore, patterns $\{o_1,o_2:1,2,4,5\}$,
%$\{o_3,o_4,o_5:2,3\}$ and $\{o_5,o_6,4,5\}$ are found. Taking

%We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
%The temporal dimension is discretized into six snapshots. 
%In each snapshot, the objects are clustered as shown in the dotted circle.
%By setting $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
%\emph{Convoy} pattern finds the objects that travels in consecutive timestamps. Only one object group $\{o_3,o_4\}$
%matches the criteria with the timestamps $\{1,2,3\}$. Since the example treats the clusters as given, \emph{flock}
%shares the same pattern result \emph{convoy}.  When the consecutiveness constraint is relax, we discover more patterns.
%By setting $L = 2$, we find three \emph{group} patterns. For example $\{o_1,o_2\}$ forms a \emph{group} pattern
%since they appear together in $\{1,2,4,5\}$, where the local consecutiveness of size $2$ ($L = 2$) is met.

%It is worth noting that \emph{convoy} and \emph{flock} have the same result pattern because both patterns share 
%the same constraints on the time duration. I DON'T UNDERSTAND WHY YOU EMPHASIZE THIS. WHEN WILL THEY BE DIFFERENT?
%The groups detected by \emph{Swarm} are superset of \emph{convoy} and \emph{flock} patterns, as \emph{Swarm} imposes no constraint on temporal consecutiveness. By setting $L=2$, we find three \emph{group} patterns. 
%If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration. TOO UGLY! NEED TO EXPLAIN THE FIGURE BASED ON TABLE $1$. AT LEAST READERS CAN HAVE A ROUGH IDEA HOW YOU OBTAIN THE RESULT GROUPS.

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. 
%Besides, we observe that, the number of co-movement patterns could be nearly exponential. 
%For instance, in the small example in Figure~\ref{fig:related_work}, \emph{swarm} already discovers 5 patterns.
We further identify that existing patterns either miss out interesting patterns (i.e, \emph{convoy}) 
or likely contain non-interesting patterns (i.e., \emph{swarm}, \emph{platoon}).
Hence, there is a particular demand for a new pattern model to fine control the pattern result without losing expressiveness. 
The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns} as well as an experimental evaluation with million-scale cardinality of a trajectory database (as shown in Figure~\ref{}). Results show that their performances degrade dramatically as the dataset size scales up and none of the existing solutions is scalable to handle large-scale trajectories.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we summarize two anomalies from existing patterns, namely, \emph{missing-pattern} and \emph{loose-connection}.
The \emph{missing-pattern}~\cite{li2010swarm} anomaly arises due to the stringent constraints on the duration of a pattern. As shown in 
Figure~\ref{fig:platoon_weakpoint} (a). if the duration size is set to be $K=4$, neither \emph{flock}s nor \emph{convoy}s
can be discovered. As we notice, object $o_1$ is temporally far from $o_2$ at timestamp $4$, which is likely to be
the result of errors in interpretation of missing points, or $o_1$ faces traffic control at time $4$. Such an anomaly can
be resolved by \emph{swarm} and \emph{platoon} due to a relaxed constraint on the duration. However, 
\emph{swarm} and \emph{platoon}'s relaxations encompass a type of non-interesting patterns which is referred
as \emph{loose-connection}~\cite{li2015platoon} anomaly. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
the two objects $o_1, o_2$ 
would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
duration is $98$ timestamps apart, making the co-movement behavior very weak.
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. In current literature,
users are unable to explicitly exclude the loosely-connected patterns even when those patterns are unwanted.
%When such loosely-connected patterns are unwanted, users currently are unable to directly control the outputs.
To cope with both of the two anomalies, we propose the \emph{general co-movement pattern} 
by introducing the gap parameter $G$, which requires the distance of 
timestamps in the duration to be no larger than $G$. 
By so doing, we gain a fine-grained control over the pattern duration, which alleviates both the \emph{missing-pattern} and the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. Therefore, users are still able to exclude non-consecutive patterns 
or include loosely-connected patterns when they feel necessary.
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?

%
\begin{figure}[h]
\center
\includegraphics[width=0.4\textwidth]{platoon_weakpoint.eps}
\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
in \emph{flock} and \emph{convoy}. When $K=4$, none of the two patterns can be discovered. (b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
\label{fig:platoon_weakpoint}
\end{figure}

@@

We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

### 2016-05-14 sec4_system.tex
Introduction Almost Done
Need resolve comments

\subsection{Preliminary on MapReduce}
MapReduce (MR) was formally proposed by Dean et. al.~\cite{dean2008mapreduce}
and has subsequently implemented by many open source systems. Those systems
provide handy APIs with fualt tolerances and are popularly
used as large-scale data processing platforms. 
% become a ubiquitous parallel platform for large-scaled data processing. 
%Current open source MapReduce systems provide handy programming APIs with fault tolerances
%in backends. Such systems include Hadoop, Shark and Spark to name a few.
In simple words, there are two conceptual types of computing nodes in MR,
namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
algorithm consists of two stages: First, input data
are partitioned and read by a \emph{map} function on each mapper. Mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Second,
reducers process the received data using a \emph{reduce} function then write the
outputs.

Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
First, since reducers are required to be independent, partitioning  
data to fit the independence could be challenging. Second, since the \emph{shuffle}
stage requires network access, the data been shuffled should be minimized. 
We take these concerns in consideration when designing our solutions for mining GCMP.
%We would bare this concerns in designing our GCMP mining algorithm.
%a natural
%problem is how to partition the data in map and shuffle phase so that reducers 
%achieve the independence.
%
%A critical question in designing a MapReduce algorithm is how to make 
%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
%requires data processed at each reducer to be independent.
%
%Since the \emph{shuffle} stage needs to transfer data over network, 
%an important attention to pay during designing MapReduce an algorithm is 
%to minimize the shuffle amounts and shuffle counts.

\subsection{MapReduce Processing for Mining GCMP}
Our GCMP mining process consists of two MR jobs, which are further
divided into four MR stages as illustrated in Figure~\ref{fig:overview}.
The first MR job is to cluster objects at each snapshot (i.e.,
 $\forall t, o,$ compute $C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
in map phase, trajectories are first reorganized by timestamps and object locations
at the same timestamps form a cluster. In reduce phase, clustering of objects at each
snapshot is processed independently. The second MR job is to mine GCMPs from 
clusters in each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
the purpose of comparison. Both the two algorithms would partition snapshots in map phase
(as in Figure~\ref{fig:overview}(c))
and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).

@@

Although we need two MR jobs to complete the GCMP mining task, 
it is easy to pipeline the two jobs to exploit data locality.
Specifically, the reducer output at step (b) can be directly reused 
as the input to the mappers at step (c). Therefore we do not need to 
transfer data between the two jobs. Modern MR platforms, especially Spark, have
already supported such a kind of pipeline by default.

@@

%Depends on the pattern mining strategy, the size of shuffle and replication may differ. We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.

%
%In particular, we need
%the number of partitions to be reasonably large in order to achieve
%good parallelism in stage (d). Meanwhile, we need to ensure a partition 
%of snapshots containing enough information so that patterns discovered 
%in stage (d) are complete.  Furthermore, we have to ensure that the
%patterns that discovered in stage (d) are real patterns.

%However, there are two conflicting requirements that restrain us from 
%designing a simple and effective solution. 
%On one hand, we need to partition snapshots in stage (c) as many as possible 
%so that good parallelism could be achieved in stage (d). 
%On the other hand, in stage (d), 
%we require each partition containing enough information in order to discover
%proper GCMP patterns. This prevents us from arbitrarily partition snapshots in
%stage (d). To design a working algorithm, find the minimum size of partition is
%crucial. In the following section, we first design a naive approach that
%partitions snapshots by allowing overlapping among partitions. Such a partition strategy
%although has overhead in shuffling, it corrects find GCMPs in parallel in stage (d).
%In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.

%\section{Temporal Replication and Mining}
%
%
%%It is notable that some patterns 
%%may be very long in duration (e.g., when discovering \emph{swarm}) or some patterns 
%%may contain a large set of objects (e.g., when discover \emph{group} patterns with small $L$).
%%Therefore, we require the size of partition to be large enough. Reaching the
%%balance between the two requirement is crucial. In the following sections, we will
%%describe a naive partition scheme which meets the two requirements.
%
%%Our parallel solution incurs two rounds of shuffles. The first round of shuffle happens in step (a). This
%%is because that the trajectories stored in HDFS needs to be regrouped to form snapshots. 
%%The second round of shuffle occurs in step(d). This is because that 
%% the clusters need to be regrouped so that subsequent pattern detection can be performed.
%% Despite the simpleness of our parallel solution, it is actually nontrivial to work out a scalable solution.
%% The major challenge lies in the step (d) and (e). 
%
%
%%\section{Preliminary on Apache Spark}
%%\label{sec:system_overview}
%%Apache Spark is an open sourced modern parallel processing platform
%%based on Resilient-Distributed-Dataset (RDD). Each RDD is able to take an action (including Map, Reduce, GroupByKey etc.) and then transforms to a new RDD. Algorithms in Spark is implemented by supplying various actions to an input RDD. Each RDD in Spark has a pre-defined and fixed number of partitions, where each partition forms a task assigned to an executor.
%%
%%Compared to MapReduce, Spark 
%%utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}. In order to fully utilize the memory, Spark creates one thread for each task and then multiple tasks belonging to the same JVM share the available memory.
%Due to threading, there is a paradigm shift from MapReduce to Spark. In MapReduce, the cost of starting a task is expensive, as each task in MapReduce requires a dedicated JVM process. While in Spark, the cost of starting a task is negligible since each task is done by a thread.  Therefore in Spark, we may create many more parallel tasks than in MapReduce before reaching to the system limitation.

%\section{Mining Generalized Co-moving Pattern}
%\label{sec:solution}
%There are two stages in mining GCMP. The first stage is to cluster objects in each snapshots. Then the seconds stage is to mine patterns from clusters in parallel. The overview of the parallel approach is 
%shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
%read trajectories and cluster objects in the same snapshots. Since the objects at each snapshots are independent, this stage can be easily performed in parallel. The first stage involves network IO. Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.

>>>>

\subsection{Preliminary on MapReduce}
MapReduce (MR) was formally proposed by Dean et.al.~\cite{dean2008mapreduce}
and has subsequently implemented by many open source systems. Those systems
provide handy APIs with fault tolerances and are popularly
used as large-scale data processing platforms. 
% become a ubiquitous parallel platform for large-scaled data processing. 
%Current open source MapReduce systems provide handy programming APIs with fault tolerances
%in backends. Such systems include Hadoop, Shark and Spark to name a few.
In simple words, there are two conceptual types of computing nodes in MR,
namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
algorithm consists of three major steps: First, input data
are partitioned and read by a \emph{map} function on each mapper. Then, mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Lastly,
reducers process the received data using a \emph{reduce} function.

Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
First, since reducers are required to be independent, partitioning  
data to fit the independence could be challenging. Second, since the \emph{shuffle}
step requires network access, the data been shuffled should be minimized. 
We take these concerns in consideration when designing our solutions for mining GCMP.
%We would bare this concerns in designing our GCMP mining algorithm.
%a natural
%problem is how to partition the data in map and shuffle phase so that reducers 
%achieve the independence.
%
%A critical question in designing a MapReduce algorithm is how to make 
%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
%requires data processed at each reducer to be independent.
%
%Since the \emph{shuffle} stage needs to transfer data over network, 
%an important attention to pay during designing MapReduce an algorithm is 
%to minimize the shuffle amounts and shuffle counts.

\subsection{MapReduce Processing for Mining GCMP}
Our GCMP mining process consists of two MR jobs as illustrated in Figure~\ref{fig:overview}.
The first MR job is to cluster objects at each snapshot (i.e.,
 $\forall t, o,$ compute $C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
in map phase, trajectories are firstly reorganized by timestamps and object locations
at the same timestamps form a snapshot. In reduce phase, clustering of objects at each
snapshot is processed independently. The second MR job is to mine GCMPs from 
clusters in each snapshot. We design and compare two MR algorithms (i.e., TRM and SPM)for 
GCMP mining. Both the two algorithms would partition snapshots in map phase
(as in Figure~\ref{fig:overview}(c))
and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).

@@

Although we need two MR jobs to complete the GCMP mining task, 
it is easy to pipeline the two jobs to exploit data locality.
Specifically, the reducer output at step (b) can be directly reused 
as the input to the mappers at step (c). Therefore we do not need to 
transfer data between the two jobs. Modern MR platforms, especially Spark, have
already supported such a kind of pipeline.

@@
